% JB Hi-Fi specific cover letter
\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.2cm,bottom=1.5cm]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\input{../shared/fonts.sty}
\PassOptionsToPackage{hidelinks}{hyperref}\usepackage{hyperref}\usepackage{bookmark}
\urlstyle{same}\usepackage{enumitem}\usepackage{xcolor}\usepackage{titlesec}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\input{../shared/colors.sty}

% Contact Block
\makeatletter
\providecommand{\ContactBlock}{}
\renewcommand{\ContactBlock}{%
  {\Large \textbf{Aaron De Vries}}\par
  {\color{MidBlue}\small
  \faIcon{map-marker-alt}\, Homebush, NSW \quad\textbar\quad
  \faIcon{phone}\, \href{tel:+61400375308}{0400 375 308} \quad\textbar\quad
  \faIcon{envelope}\, \href{mailto:aarondevries@protonmail.com}{aarondevries@protonmail.com} \quad\textbar\quad
  \faIcon[brands]{linkedin}\, \href{https://linkedin.com/in/aarondevriesdev}{linkedin.com/in/aarondevriesdev}%
  }\par
}
\makeatother

\begin{document}
\ContactBlock

\vspace{1em}

\today

\vspace{1em}

Dear JB Hi-Fi Burwood Team,

I am writing to express my strong interest in retail positions at JB Hi-Fi Burwood, where I can leverage my extensive customer service experience and genuine passion for consumer electronics and technology.

With over 8 years of retail experience at Dick Smith Electronics and Big W, I have developed strong skills specifically aligned with JB Hi-Fi's customer-focused environment. My background spans consumer electronics, home entertainment, gaming, and technology products across diverse customer groups.

Key highlights that make me an excellent fit for JB Hi-Fi include:
\begin{itemize}
\item Exceptional customer service and result-driven sales in consumer electronics and entertainment
\item Deep passion for technology, gaming, music, and home entertainment systems
\item POS system operation, cash handling, and high-volume transaction processing
\item Merchandising and inventory management in fast-paced retail environments
\item Team collaboration, training, and mentoring experience
\item Strong product knowledge and enthusiasm for helping customers find the right solutions
\end{itemize}

What excites me most about JB Hi-Fi is the opportunity to combine my retail expertise with my genuine enthusiasm for technology and entertainment. I stay current with the latest gaming trends, audio equipment, and consumer electronics, which enables me to provide knowledgeable recommendations and exceptional customer experiences.

I am particularly drawn to JB Hi-Fi's customer-centric culture and would welcome the opportunity to contribute to your team's continued success. I am available for immediate start and would love to discuss how my experience and passion align with JB Hi-Fi's values.

Thank you for considering my application. I look forward to hearing from you.

Sincerely,

Aaron De Vries

\end{document}
