
\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.4cm]{geometry}\setlength{\parindent}{0pt}\setlength{\parskip}{4pt}
\usepackage[T1]{fontenc}\usepackage{lmodern}\usepackage{microtype}
\PassOptionsToPackage{hidelinks}{hyperref}\usepackage{hyperref}\urlstyle{same}
\usepackage{xcolor}\usepackage{titlesec}\definecolor{DeepBlue}{HTML}{123262}
\titleformat{\section}{\large\scshape\raggedright\color{black}}{}{0em}{}[\vspace{0.2\baselineskip}{\color{DeepBlue}\titlerule}\vspace{0.1\baselineskip}]
\begin{document}
\section*{Personal Details}
\textbf{Name:} Aaron De Vries \hfill \textbf{Location:} Homebush, NSW\\
\textbf{Email:} \href{mailto:azzad10@gmail.com}{azzad10@gmail.com} \hfill \textbf{Phone:} \texttt{XXX XXX XXX}
\section*{Availability}
I'm available for an immediate start. Preferred availability: Monday–Sunday, flexible across weekdays and weekends. I can work late-night trade and public holidays as required. Open to 15–30 hours per week initially, with additional hours during peak periods.
\section*{Why JB Hi-Fi Burwood?}
I love JB Hi-Fi's energy and product range. The Burwood opening is a chance to help set first impressions—tidy merchandising, accurate ticketing, and consistent customer-first service. My background in consumer electronics means I can confidently serve customers across audio, TV, computing, and gaming from day one.
\section*{Customer Service Example}
A customer needed a laptop for uni with strict budget and battery requirements. I asked a few questions about software and portability, shortlisted two models, and explained trade-offs in simple terms. I paired the laptop with a student-friendly backpack and a discounted USB-C hub. The customer returned later to thank me for the clear advice—this reinforced the value of listening first, recommending second.
\section*{Handling Peak Trading}
During catalogue launches at Big W, queues grew quickly. I stepped to POS to keep lines moving, prepped gift cards and cash drawers in advance, and coordinated with the floor to prioritise fast sellers. Calm communication and quick decisions kept wait times down and customers positive.
\section*{Teamwork}
I enjoy being a reliable teammate. At Dick Smith I helped onboard a new casual by walking through device setup, ticketing, and daily recovery. Clear handovers reduced missed tasks and improved shift transitions.
\section*{Integrity and Loss Prevention}
I follow store procedures carefully—especially for returns, warranties, and high-value items. I double-check serials and ensure documentation is accurate. On the floor I keep an eye on blind spots and communicate discreetly if something looks off.
\section*{Merchandising and Standards}
I’m detail-oriented with planograms and promo sets. I keep ticketing current to prevent price disputes, group related items to support add-ons, and face-up shelves regularly to maintain a clean look.
\section*{Technology Interest}
I keep up with new headphones, gaming accessories, Bluetooth speakers, and entry-level laptops/Chromebooks. I like testing demo units so I can explain features in customer language rather than jargon.
\section*{Availability for Training}
I can attend induction and training sessions at short notice and am comfortable learning new systems quickly.
\section*{Additional Information}
I have retail POS, cash handling, and BOH experience; I’m punctual, friendly, and enjoy helping customers find the right fit. I’m excited to contribute to a great opening for JB Hi-Fi Burwood.
\end{document}
