
\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.1cm]{geometry}
\setlength{\parindent}{0pt}\setlength{\parskip}{3pt}
\usepackage[T1]{fontenc}\usepackage{lmodern}
\PassOptionsToPackage{hidelinks}{hyperref}\usepackage{hyperref}\urlstyle{same}
\usepackage{enumitem}\usepackage{xcolor}\usepackage{titlesec}
\input{../shared/colors.sty}

\titleformat{\section}{\large\scshape\raggedright\color{black}}{}{0em}{}[\vspace{0.25\baselineskip}{\color{MidBlue}\titlerule}\vspace{0.1\baselineskip}]
\titlespacing*{\section}{0pt}{0.6\baselineskip}{0.35\baselineskip}
% --- Inline Contact Block (FontAwesome5 + clickable links) ---
\makeatletter
\providecommand{\ContactBlock}{}
\renewcommand{\ContactBlock}{%
  {\Large \textbf{Aaron De Vries}}\par
  {\color{MidBlue}\small
  \faIcon{map-marker-alt}\, Homebush, NSW \quad\textbar\quad
  \faIcon{phone}\, \href{tel:+61400375308}{0400 375 308} \quad\textbar\quad
  \faIcon{envelope}\, \href{mailto:aarondevries@protonmail.com}{aarondevries@protonmail.com} \quad\textbar\quad
  \faIcon[brands]{linkedin}\, \href{https://linkedin.com/in/aarondevriesdev}{linkedin.com/in/aarondevriesdev}%
  }\par
}
\makeatother
% --- End Inline Contact Block ---
\begin{document}
\ContactBlock

\section*{About Me}
Passionate, customer-focused, and results-driven retail team member offering extensive experience in sales, customer service, consumer electronics, IT, entertainment, and appliances.

\begin{flushright}
Homebush, NSW \\
19 September 2025
\end{flushright}

\begin{flushright}
Homebush, NSW \\
19 September 2025
\end{flushright}
Hiring Manager \\
JB Hi-Fi Burwood \\\\[0.6\baselineskip]
Dear Hiring Manager, \\\\[0.4\baselineskip]
I'm excited to apply for the Retail Team Member role at JB Hi-Fi Burwood. With hands-on experience in consumer electronics at Dick Smith and Big W, I know how to deliver great service, run POS during busy trading, and maintain strong merchandising and stock standards.
What excites me most is contributing to the opening of a brand-new JB Hi-Fi store. First impressions shape loyalty and reputation. I'm keen to help set a positive, customer-first culture from day one so Burwood customers immediately associate the new location with trusted service and expertise.
I bring a mix of retail know-how and IT experience that makes me confident with tech. I've exceeded sales targets, solved customer problems, and built repeat business. My software engineering background sharpened my problem-solving and teamwork—ideal for fast-paced environments.
Most importantly, I genuinely love technology, entertainment, gaming, and music—passions that match JB Hi-Fi's culture. I'd love to bring my energy to your new Burwood team and help build a strong foundation for lasting success.
I look forward to hearing from you.
\vspace{0.8\baselineskip}
Sincerely, \\
Aaron De Vries

\end{document}
