% Promoted from JB Blue to be the default main resume
% Source: resume/jb/Resume_JBHiFi_Burwood_Blue_Final.tex
\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.2cm,bottom=1.5cm]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\input{../shared/fonts.sty}
\PassOptionsToPackage{hidelinks}{hyperref}\usepackage{hyperref}\usepackage{bookmark}
\urlstyle{same}\usepackage{enumitem}\usepackage{xcolor}\usepackage{titlesec}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}\input{../shared/colors.sty}

\titleformat{\section}{\large\scshape\raggedright\color{black}}{}{0em}{}[\vspace{0.25\baselineskip}{\color{MidBlue}\titlerule}\vspace{0.1\baselineskip}]
\titlespacing*{\section}{0pt}{0.55\baselineskip}{0.3\baselineskip}
% --- Inline Contact Block (FontAwesome5 + clickable links) ---
\makeatletter
\providecommand{\ContactBlock}{}
\renewcommand{\ContactBlock}{%
  {\Large \textbf{Aaron De Vries}}\par
  {\color{MidBlue}\small
  \faIcon{map-marker-alt}\, Homebush, NSW \quad\textbar\quad
  \faIcon{phone}\, \href{tel:+61400375308}{0400 375 308} \quad\textbar\quad
  \faIcon{envelope}\, \href{mailto:aarondevries@protonmail.com}{aarondevries@protonmail.com} \quad\textbar\quad
  \faIcon[brands]{linkedin}\, \href{https://linkedin.com/in/aarondevriesdev}{linkedin.com/in/aarondevriesdev}%
  }\par
}
\makeatother
% --- End Inline Contact Block ---
\begin{document}
\ContactBlock

\section*{About Me}
Passionate, customer-focused, and results-driven retail team member offering extensive experience in sales, customer service, consumer electronics, IT, entertainment, and appliances.


\section*{Key Skills}
\begin{itemize}[nosep,leftmargin=*,topsep=0pt,partopsep=0pt,itemsep=3pt]
\item Customer service and result-driven sales in consumer electronics and home entertainment
\item POS system operation, cash handling, and high-volume transaction processing
\item Merchandising, inventory management, stock receiving, and back-of-house processes
\item Team collaboration, training, and performance support
\item Technology, IT, and appliances expertise across diverse customer groups
\item Loss prevention and store security awareness
\item Effective communication with enthusiasm and customer focus
\end{itemize}
\section*{Retail Experience}
\textbf{Retail Team Member} \textbar\ Dick Smith Electronics --- Roselands, NSW \hfill \textit{Nov 2012--Mar 2016}
\begin{itemize}[nosep,leftmargin=*,topsep=0pt,partopsep=0pt,itemsep=3pt]
\item Delivered exceptional customer experiences in consumer electronics across pre-sale consultation, transaction processing, and post-sale support.
\item Processed stock deliveries efficiently, following established store procedures and inventory management protocols.
\item Handled sales floor operations including pricing, merchandising, and back-of-house tasks to enhance customer experience and brand presentation.
\item Set up and maintained promotional floor displays for key electronics brands to drive sales and highlight new products.
\item Delivered tailored solutions in customer-facing roles, demonstrating strong communication skills with diverse customer groups.
\item Trained and mentored new team members, fostering teamwork and a high-performance culture.
\end{itemize}
\textbf{Retail Team Member} \textbar\ Big W --- Miranda, NSW \hfill \textit{Sep 2005--Jan 2012}
\begin{itemize}[nosep,leftmargin=*,topsep=0pt,partopsep=0pt,itemsep=3pt]
\item Specialized in customer-facing retail sales and merchandising within home entertainment, technology, and appliances sectors.
\item POS system operation, cash handling, and high-volume transaction processing
\item Maintained pricing accuracy and efficient stock delivery processes, and proactively implemented loss prevention strategies to reduce shrinkage and protect store assets.
\item Delivered exceptional customer service with enthusiasm and customer focus across diverse customer groups.
\item Collaborated effectively with team members in fast-paced retail operations to ensure smooth store operations and support customer needs.
\end{itemize}
\section*{Other Professional Experience}
\textbf{Senior Software Engineer} \textbar\ Avaloq --- Sydney, NSW \hfill \textit{Jul 2016--Nov 2024}
\begin{itemize}[nosep,leftmargin=*,topsep=0pt,partopsep=0pt,itemsep=3pt]
  \item Collaborated effectively in fast-paced, customer-focused teams; adapted to changing priorities.
  \item Applied problem-solving skills to support team goals and enhance customer satisfaction.
\end{itemize}
\textbf{Application \& Web Developer} \textbar\ Bond International Software --- Wollongong, NSW \hfill \textit{Aug 2014--Jun 2016}
\begin{itemize}[nosep,leftmargin=*,topsep=0pt,partopsep=0pt,itemsep=3pt]
  \item Partnered with clients to improve user experiences through technical solutions and support.
\end{itemize}
\section*{Education}
\textbf{Bachelor of Computer Science} \\
Major: Software Engineering \& Enterprise Systems Development \\
University of Technology Sydney, 2012
\section*{Additional Information}
\begin{itemize}[nosep,leftmargin=*,topsep=0pt,partopsep=0pt,itemsep=3pt]
\item Passionate about technology, music, gaming, and continuous learning.
\item Available for immediate start. References available on request.
\end{itemize}

\end{document}
